### 2021-04-15 paper.Rmd
Some comments about Figures, included in Issues too

@@

>>>>

<!-- Figure 4:   Huber's plot (left plots) of the penguins data....Maybe will be better to  capital letter for axis labels (Count, Group and Best projected data). And maybe use the same Dark2 palette. -->

@@

<!-- Figure 6: "A comparison of guided....." and Figure 7:"Still views of a tour showing the space...." maybe change the color (brown) because are difficult to distinguish. Similar problem in Figure 12: Three  projections  from  a  manual  tour  where  variable  "bl" .... "  Not sure if you have selected a colorblind friendly palette but I check these Figures with a colorblind person (small sample but...) and was very  difficult  for him to distinguish the mixed colors.  -->
